A Reduced Order Model for Porous Media Flows: Coupling Linear Regression with Principal Component Analysis (PCA) using High-Order Singular Value Decomposition (HOSVD) in Upscaling Calculations for Permeability in Reservoir Simulations

### 2018-12-03 Papers/AppliedMaths2018/Resubmission/Stochastic_Upscaling_UK_AMM_2018b.tex
files to be modified in the next 250min

\citet{Yeo2001} discussed the accuracy of renormalization method for upscaling 2D hydraulic conductivity fields for two cases. Both cases employed the $4$-quadrant model (see Section~\ref{subsection:model} for details) set-up. The first case had low permeablitity in all the blocks except the bottom right block which had high permeability, while the second case employed the checkboard style described in Section~\ref{subsection:model}. Different conductivity ratios were also investigated for the two cases. The conclusion drawn was that renormalization worked fairly well for the first case, but very poorly for the second case.

>>>>

\citet{Yeo2001} discussed the accuracy of renormalization method for upscaling 2D hydraulic conductivity fields for two cases. Both cases employed the $4$-quadrant model (see Section~\ref{subsection:model} for details) set-up. The first case had low permeability in all blocks except the bottom right block which had high permeability, while the second case employed the check-board style described in Section~\ref{subsection:model}. Different conductivity ratios were also investigated for the two cases. The conclusion drawn was that renormalization worked fairly well for the first case, but very poorly for the second case.
